An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-08 main.tex
Further fix to abbreviations.

Overall the main fixation probabilities of interest are \(x_1\) and \(x_{N-1}\), these
reflect a strategy's ability to invade or resist invasion; for \(N=2\) these two cases
coincide. Figure~\ref{fig:fixation_heatmap_2} shows
all pairwise fixation probabilities for strategies on the vertical column when
being matched against probabilities on the horizontal column. This is summarised
in Figure~\ref{fig:boxplot_2} and Table~\ref{tbl:summary_top_2}.

@@

\begin{figure}[!hbtp]
    \begin{subfigure}[t]{.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./img/fixation_heatmap_2_invade.pdf}
        % TODO Remove this: I don't feel it is effective.
        \caption{The pairwise fixation probabilities for \(N=2\)}
        \label{fig:fixation_heatmap_2}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.6\textwidth}
        \centering
        \includegraphics[height=.8\textheight]{./img/boxplot_2_invade.pdf}
        \caption{The median fixation probabilities for \(N=2\)}
        \label{fig:boxplot_2}
    \end{subfigure}
\end{figure}

@@

In the next sections we pay close attention to
strategies who are strong invaders/resistors and shown diagrammatically in
Figure~\ref{fig:invasion_resistance}.

\begin{figure}[!hbtp]
    \centering
    \input{./tex/invasion_resistance.tex}
    \caption{A single individual will successfully invade the population with
    probability \(x_1\). The group of Individuals will successfully resist with
    probability \(x_{N-1}\)}
    \label{fig:invasion_resistance}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Cooperator_fitness.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Defector_fitness.pdf}
        \caption{Alternator and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Tit_For_Tat_fitness.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Cooperator_v_Tit_For_Tat_fitness.pdf}
        \caption{Cooperator and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_Cooperator_fitness.pdf}
        \caption{Defector and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_Tit_For_Tat_fitness.pdf}
        \caption{Defector and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Win-Stay_Lose-Shift_v_Tit_For_Tat_fitness.pdf}
        \caption{Win Stay Lose Shift and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Win-Stay_Lose-Shift_fitness.pdf}
        \caption{Alternator and Win Stay Lose Shift}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_Win-Stay_Lose-Shift_fitness.pdf}
        \caption{Defector and Win Stay Lose Shift}
    \end{subfigure}%
    \caption{Estimated relative fitness
             for \textbf{deterministic} strategies}
    \label{fig:comparison_deterministic}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_Cooperator_fitness.pdf}
        \caption{Random and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_Defector_fitness.pdf}
        \caption{Random and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_Tit_For_Tat_fitness.pdf}
        \caption{Random and Tit For Tat}
    \end{subfigure}%

@@

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Calculator_v_ALLCorALLD_fitness.pdf}
        \caption{Calculator and All C or all D}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Arrogant_QLearner_fitness.pdf}
        \caption{Calculator and Arrogant Q learner}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Tit_For_Tat_fitness.pdf}
        \caption{All C or all D and Tit For Tat}
    \end{subfigure}%
    \caption{Estimated relative fitness
             for \textbf{stochastic} strategies}
    \label{fig:comparison_stochastic}
\end{figure}

>>>>

Overall the main fixation probabilities of interest are \(x_1\) and \(x_{N-1}\), these
reflect a strategy's ability to invade or resist invasion; for \(N=2\) these two cases
coincide. Figure~\ref{fig:boxplot_2} shows
all fixation probabilities for the strategies considered. This is summarised
in Table~\ref{tbl:summary_top_2}.

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.8\textheight]{./img/boxplot_2_invade.pdf}
    \caption{The fixation probabilities for \(N=2\)}
    \label{fig:boxplot_2}
\end{figure}

@@

In the next sections we pay close attention to
strategies who are strong invaders/resistors.

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Cooperator_fitness.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Defector_fitness.pdf}
        \caption{Alternator and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_TfT_fitness.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Cooperator_v_TfT_fitness.pdf}
        \caption{Cooperator and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_Cooperator_fitness.pdf}
        \caption{Defector and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_TfT_fitness.pdf}
        \caption{Defector and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/WSLS_v_TfT_fitness.pdf}
        \caption{Win Stay Lose Shift and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_TfT_fitness.pdf}
        \caption{Alternator and Win Stay Lose Shift}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_WSLS_fitness.pdf}
        \caption{Defector and Win Stay Lose Shift}
    \end{subfigure}%
    \caption{Estimated relative fitness
             for \textbf{deterministic} strategies}
    \label{fig:comparison_deterministic}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_Cooperator_fitness.pdf}
        \caption{Random and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_Defector_fitness.pdf}
        \caption{Random and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_TfT_fitness.pdf}
        \caption{Random and Tit For Tat}
    \end{subfigure}%

@@

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Calculator_v_ALLCorALLD_fitness.pdf}
        \caption{Calculator and All C or all D}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Arrogant_QLearner_fitness.pdf}
        \caption{Calculator and Arrogant Q learner}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_TfT_fitness.pdf}
        \caption{All C or all D and Tit For Tat}
    \end{subfigure}%
    \caption{Estimated relative fitness
             for \textbf{stochastic} strategies}
    \label{fig:comparison_stochastic}
\end{figure}
